Labeled Tweets

### 2019-12-20 Code/03_analyze_complaint_categories.Rmd

# Read in the Labeled Tweets
```{r}
# Note that the labeled tweet data is kept in my Temporary folder in the train_test_data folder
data <- read_csv("../../Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")
```

>>>>

# Read in the Labeled Tweets
```{r}
# Note that the labeled tweet data is kept in my Temporary folder in the train_test_data folder
data <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv"))
```
